Relevance-based Quantization of Scattering Features for Unsupervised Mining of Environmental Audio

### 2018-02-15 paper/structureScene.tex
the verb utilize should be avoided
comments on writing

%we can emulate their selection behavior by quantizing the auditory scene and defining a distance over this quantization.
We also propose a new model for acoustic scenes, where the signal is represented at sub-second scales by scattering transforms, while larger scales are captured by an unsupervised method that quantizes the scattering coefficients into a given number of clusters. We then use these clusters to define a set of distances that can subsequently be used for similarity retrieval. Testing this approach on a scene retrieval task, we obtain significant improvements over traditional bag-of-frames and summary statistics models applied both to MFCCs and scattering coefficients.

@@

The evaluation is performed on the private part of the DCASE 2013 dataset. The metric used is the precision at rank $k$ ($p@k$), which is computed by taking a query item and counting the number of items of the same class within the $k$ closest neighbors, and then averaging over all query items. These closest neighbors are determined by a particular distance, which is one of \emph{RbQ-c}, \emph{RbQ-a}, or \emph{RbQ-w}.

The metric $p@k$ is computed for $k=\lbrace 1,\ldots,9\rbrace$, since each class only has $10$ items. Note that a $p@1$ is equivalent to the classification accuracy obtained by the classifier which chooses the label of the closest neighbor for a given item. The \emph{RbQ} approaches are compared to commonly used early integration approach \emph{early}, which consists in averaging over time the feature set of each scene, resulting in one feature vector per scene. The parameters of the BOF approach are the one used in \cite{aucouturier2007bag}, \textit{i.e.} 10 Gaussians per scene estimated using the Expectation Maximization (EM) algorithm. Gaussian models are compared using Monte-Carlo sampling approaximation. In order to ensure convergence of the EM algorithm when considering the scattering features as input, the dimension of the feature vector is reduced from 1367 to 30 by projecting the features over the 30 principal components computed over the whole dataset.

@@

This paper presents a new approach for modeling acoustic scenes which utilizes scattering transforms at small scales and a cluster-based representation at large scales. Compared to traditional models based on BOF and summary statistics, this representation allows for the characterization of distinct sound events superimposed on a stationary texture, a concept which has strong grounding in the cognitive psychology literature. In order to extend the selectivity potential of late integration using SVMs to the unsupervised case, we develop the cluster-based model and validate it using experiments on acoustic scene similarity retrieval. For this task, we show significant improvements over the traditional BOF and summary statistics models based on both standard MFCCs and scattering features.
These outcomes shall be studied further in future work by considering larger databases and emerging tasks in computational bioacoustics \cite{wimmer2013sampling}.

>>>>

%we can emulate their selection behavior by quantizing the auditory scene and defining a distance over this quantization.
We also propose a new model for acoustic scenes, where the signal is represented at sub-second scales by scattering transforms, while larger scales are captured by an unsupervised method that quantizes the scattering coefficients into a given number of clusters. We then use these clusters to define a set of distances that can subsequently be used for similarity retrieval. \vl{The verb use is repeated in the previous sentence.} Testing this approach on a scene retrieval task, we obtain significant improvements over traditional bag-of-frames and summary statistics models applied both to MFCCs and scattering coefficients.

@@

The evaluation is performed on the private part of the DCASE 2013 dataset. The metric used is the precision at rank $k$ ($p@k$), which is computed by taking a query item and counting the number of items of the same class within the $k$ closest neighbors, and then averaging over all query items. These closest neighbors are determined by a particular distance, which is one of \emph{RbQ-c}, \emph{RbQ-a}, or \emph{RbQ-w}. \vl{Avoid passive voice.}

The metric $p@k$ is computed for $k=\lbrace 1,\ldots,9\rbrace$, since each class only has $10$ items. Note that a $p@1$ is equivalent to the classification accuracy obtained by the classifier which chooses the label of the closest neighbor for a given item. The \emph{RbQ} approaches are compared to commonly used early integration approach \emph{early}, which consists in averaging over time the feature set of each scene, resulting in one feature vector per scene. The parameters of the BOF approach are the one used in \cite{aucouturier2007bag}, \textit{i.e.} 10 Gaussians per scene estimated using the Expectation Maximization (EM) algorithm. Gaussian models are compared using Monte-Carlo sampling approaximation. In order to ensure convergence of the EM algorithm when considering the scattering features as input, the dimension of the feature vector is reduced from 1367 to 30 by projecting the features over the 30 principal components computed over the whole dataset. \vl{Too much passive voice, too many instances of "use", "used".}

@@

This paper presents a new approach for modeling acoustic scenes which utilizes scattering transforms at small scales and a cluster-based representation at large scales. Compared to traditional models based on BOF and summary statistics, this representation allows for the characterization of distinct sound events superimposed on a stationary texture, a concept which has strong grounding in the cognitive psychology literature. In order to extend the selectivity potential of late integration using SVMs to the unsupervised case, we develop the cluster-based model and validate it using experiments on acoustic scene similarity retrieval. For this task, we show significant improvements over the traditional BOF and summary statistics models based on both standard MFCCs and scattering features.
These outcomes shall be studied further in future work by considering larger databases and emerging tasks in computational bioacoustics \cite{wimmer2013sampling}.
\vl{The verb utilize should be avoided.}
